A Constraint Solving Approach to Parikh Images of Regular Languages

### 2022-07-07 main.tex
First stab at correctness proof

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  A common problem in string constraint solvers is computing the Parikh image, a
   set of linear equations that describe all possible combinations of character
   counts in strings of a given language. Automata-based string solvers
   frequently need to compute the Parikh image of large products (intersections)
   of nondeterministic automata, which in many operations is both prohibitively
   slow and memory-intensive. We contribute a novel understanding of how Parikh
   maps can be tackled as a constraint solving problem to solve real-world
   constraints stemming from functions on regular languages, most notably the
   length constraint. Furthermore, we show how this formulation can be
   efficiently implemented as a calculus, \Calculus{}, in an automated theorem
   prover supporting Presburger logic.  We implement \Calculus{} in a tool
   called \Catra{}, and evaluate it on constraints produced by the
   \OstrichPlus{} string constraint solver when solving \Fudge{standard string
   constraint benchmarks involving string lengths}. We show that our solution
   strictly outperforms the standard eager approach described
   in~\citeauthor{generate-parikh-image} as well as the over-approximating
   method recently described by~\citeauthor{approximate-parikh} by a wide
   marigin, and for realistic timeouts for constraint solving also the~\Nuxmv{}
   model checker.
\end{abstract}

@@

@@

We implement \Calculus{} as a theory for the \Princess{} automated theorem
prover in the tool \Catra{}. \Catra also supports using the
approximate method of \cite{approximate-parikh}, its fall-back variant adapted
from~\cite{generate-parikh-image}, and an adapter for the \Nuxmv{} model
checker~\cite{nuxmv}. Using \Catra{}, we compare \Calculus{} to the other two
back-ends on \NrBenchmarks{} Parikh automata satisfaction problems generated
\Fudge{by \OstrichPlus{}}.

@@

To keep things simple, in this first example we let $f$ be the function that
gives the length of a given string, e.g. $f\left(\text{curious and curiouser
still}\right) = 27$, and $f\left(\text{homo}\right) +
f\left(\text{morphism}\right) = f\left(\text{homomorphism}\right) = 12$, and we
let $\varphi(\MonoidElement) = \exists k \HoldsThat m = 2k + 1 \land k \geq 0$,
i.e. require that the length of the string is odd.

@@

The na\"ive approach would be to first compute the product of the automata, then
use the approach from \cite{generate-parikh-image} to find its image under $f$,
and then verify the constraints. However, we can take advantage of both the
constraints and definitions of $f$ to prune the automata before computing the
product and help reduce the blow-up.

@@

For our constraint, we will use $\TransitionCount{a} > \TransitionCount{b}$,
that is finding a count of characters in a string accepted by both automata where
there are more a:s than b:s. Since the underlying calculus is the same, we start immediately from Figure~\ref{fig:example-simplify-1}.

@@

\section{Generalised Parikh Maps}\label{sec:generalised}

@@

Observe that every homomorphism~$\Map:\: \Sigma^* \to \Monoid$ can be
represented as the composition~$h' \circ \ParikhMap$, for some
homomorphism~$h' : \Naturals^k \to M$. One of the insights underlying our
approach is that it is more efficient to directly compute a
generalised Parikh image~$\Map(\Language)$, than to first compute the
standard image~$\ParikhMap(\Language)$ followed by projection to
some property of interest.

@@

A useful example of such a simplifying morphism can express string
length, the problem that originally motivated our study of the Parikh
map. This mapping is relevant when solving constraints that combine
language membership as well as word length, for instance the formula
\begin{equation}\label{eq:stringLength}
x \in \Language_1 \wedge y \in \Language_2 \wedge |x| > |y|
\end{equation}
mentioned in the introduction. To solve this formula, let
$\Monoid = \Naturals$, and define the homomorphism~$L$ by $L(a) = 1$
for all characters~$a \in \Alphabet$. The length of a string
$s = s_1 \RepeatSum{\Concat} s_n$ is given by
$L(s) = \sum L(s_i) = 1 \RepeatSum{+} 1 = n$, and to solve
\eqref{eq:stringLength} we can instead solve the equi-satisfiable
formula~$\alpha \in L(\Language_1) \wedge \beta \in L(\Language_2)
\wedge \alpha > \beta$. This paper proposes efficient native
procedures to reason about membership constraints
like~$\alpha \in L(\Language_1)$, avoiding the computation of
the complete image~$L(\Language_1)$.

@@

Parikh images are also applicable to decide more general classes of
string constraints~\cite{ostrich-plus}. Consider, for instance, a
constraint involving the substring operation:
\begin{equation}
  \label{eq:substring}
  x \in \Language_1 \wedge \; 0 \leq n \leq m \leq |x| \wedge x[n:m] \in \Language_2
\end{equation}
in which $x$ is a string variable, $n, m$ are integer variables, and
$x[n:m]$ denotes the substring of $x$ starting at position~$n$ running
until position~$m$. This constraint belongs to an expressive fragment
of string logic that cannot be decided by most state-of-the-art string
solvers. To illustrate the decision procedure proposed in
\cite{ostrich-plus} for string constraints of this kind, suppose that
$\Language_2$ is defined by the regular
expression~$\mathtt{(ab|c)*}$. An automaton recognising this language
is shown in Fig.~\ref{fig:parikh-automata} (left).

@@

\section{A Calculus for Generalised Parikh Images}\label{sec:calculus}

@@

We present the rules of \Calculus{} for one automaton in
\cref{tbl:rules:single}. Note that we operate on sets of
formulas. Additionally, we also use the convention of splitting the
formulas into linear equations and inequalities ($\SomeInequalities$)
and other formulas ($\SomeClause$). \Fudge{need to say that we assume
  that the predicates (Im, etc.)  only occur positively.}

Note that the filtering function~$\Filter$ is evaluated symbolically in these
rules, and can in practice be read as a function from transitions to
$\Naturals$-valued terms (e.g.~\texttt{t} or~\texttt{t+1}). In our implementation \Catra{},
described in \cref{sec:implementation}, $\Filter$~is a vector of fresh variables
with the same size as~$\Transitions$.

@@

\subsubsection{The rules in Table~\ref{tbl:rules:single} are solution-preserving}

\begin{lemma}\label{lma:single-correct}
  Consider an application of one of the rules in
  Table~\ref{tbl:rules:single}, with
  premises~$\SomeClause_1, \ldots, \SomeClause_k$ and
  conclusion~$\SomeClause$. An assignment~$\beta$ satisfies the
  conclusion~$\SomeClause$ if and only if it satisfies one of the
  premises~$\SomeClause_i$.
\end{lemma}

@@

  \Expand{} unfolds the definition of the $\Image$ predicate. To show
  that the rule is solution-preserving we prove the equivalence of the
  upper and lower sets of formulas:
  \begin{itemize}
  \item Assume that $\beta$ satisfies the conclusion, which means that
    there is some accepting path
    $\Path = \PathEnumeration \in \Accepting{\Paths(\Automaton)}$ with
    $\val_\beta(\Filter(\Transition)) = \TransitionCount(\Transition,
    \Path)$ and $\val_\beta(\MonoidElement) =
    \Map(\WordOf(\Path))$. Since immediately implies that $\beta$
    satisfies $\Connected(\Automaton, \Filter)$, since a path is
    connected, and $\FlowEq(\Automaton, \Filter)$ since an accepting
    path satisfies the flow equations. The
    equation~$\MonoidElement = \sum_{\Transition \in
      \Transitions_\Automaton}\Filter(\Transition) \cdot
    \Map(\Transition)$ holds because of
    $\val_\beta(\Filter(\Transition)) = \TransitionCount(\Transition,
    \Path)$.
  \item Assume that $\beta$ satisfies the premise, which implies that
    $\val_\beta(\Filter)$ describes a consistent, connected flow of
    the automaton. By the same argument as in
    \cite{generate-parikh-image} (Section~\ref{sec:verma}), this flow
    can be mapped to an accepting path~$\Path$ of $\Automaton$ such
    that each transition~$\Transition$ occurs on $\Path$ exactly
    $\val_\beta(\Filter(\Transition))$ times. Together with the equation
    $\val_\beta(\Filter(\Transition)) = \TransitionCount(\Transition,
    \Path)$, this implies that $\beta$ satisfies $\SinglePredicateInstance$.
  \end{itemize}

@@

\subsection{The extended calculus is also correct}

Since the expanded calculus is in practice the addition of two rules with the
purpose of reducing an~$\Image$ predicate containing a product to the form
solved by the previous single-automaton rules of \cref{tbl:rules:single}, we
extend the reasoning from \cref{sec:single:correct} to the single-automaton
rules of \cref{tbl:rules:multi}.

\subsubsection{The calculus terminates}
\begin{lemma}
  The addition of the \ExpandM{} and \Materialise{} rules in \cref{tbl:rules:multi}
  maintains termination as shown in \cref{lma:single-terminates}.
\end{lemma}
\begin{proof}
  Similarly to how we previously showed that the number of possible executions
  of the \Split{} rule is bounded above by the number of transitions of an
  automaton, we can bound the number of applications of \Materialise{} by the
  (monotonically) decreasing number of automata in the product until we have
  approached the starting state for the single-automaton calculus. Trivially, we
  can eagerly apply \Materialise{} repeatedly to do so. Similarly, \ExpandM{} is
  just the generalisation of \Expand{} to multiple automata. In other words there are no possibilities of the calculus diverging.
\end{proof}

\subsubsection{The calculus implemements the homomorphic image of the product}
\begin{lemma}
  Using \Calculus{} to compute $\Image_{\Automaton_1\times\ldots\times\Automaton_k, \Map}(\Filter, \MonoidElement)$ is equivalent to using the single-automaton rules to compute $\Image_{\Automaton', \Map}(\Filter, \MonoidElement)$ where $\Automaton' = \Automaton_1\times\ldots\times\Automaton_k$.
\end{lemma}
\begin{proof}

  We perform this proof equivalent to set inclusion: by proving that neither predicate is stronger than the other, in the sense of rejecting an element that the other accepts and vice versa.

\begin{lemma}\label{lma:multi:rinclude}
  There exists no element $\MonoidElement$ such that $\Image_{\Automaton_1\times\ldots\times\Automaton_k, \Map}(\Filter, \MonoidElement) = \top$ but $\Image_{\Automaton', \Map}(\Filter, \MonoidElement) = \bot$.
\end{lemma}
\begin{proof}
  Assume that such an $\MonoidElement$ exists with the goal of deriving a
  contradiction. Under this assumption, would we be able to use the two new
  rules to close the proof goal with $\top$?

  The \ExpandM{} rule would allow us to close no goal since it only adds
  additional clauses. Our only hope is in using \Materialise{} to get rid of the
  product step by step without introducing an unsatisfiable clause. However, all
  \Materialise{} does is computing the product step by step, eventually arriving
  at $\Automaton'$ modulo permutations. Therefore, it can be no more satisfiable
  than the single-automata predicate.

  \contents{\item Do I need to worry about the fact that I have no extra
  clauses/$\SomeClause$ here? If present, I would need to apply the definition
  of \BindingSum{} since that is what transfers constraints on individual
  automata up and down the materialisation.}
\end{proof}

\begin{lemma}\label{lma:multi:linclude}
  There exists no element $\MonoidElement$ such that $\Image_{\Automaton_1\times\ldots\times\Automaton_k, \Map}(\Filter, \MonoidElement) = \top$ but $\Image_{\Automaton', \Map}(\Filter, \MonoidElement) = \bot$.
\end{lemma}
\begin{proof}
  Assume that such an element exists. Then $\MonoidElement =
  \Map(\WordOf(\Path))$ for some $\Path$ ending up in an accepting state in
  $\Automaton'$, and consistent with $\Filter$ along the transitions of $\Path$.
  Then a corresponding path must exist in each automata of $\Automaton'$,
  although possibly with different labels.

  For \ExpandM{} to introduce unsatisfiability, either of its automata must be
  disconnected (or its corresponding $\Connected{}$ predicate can be removed
  with \Propagate{}), or its flow must be infeasible. However, this contradicts
  the existence of some corresponding path $\Path$ in each automaton. Hence,
  \ExpandM{} cannot be the source of the unsatisfiability.

  The same applies for the second half of \Materialise{}, if the corresponding
  path exists in each individual automaton and in $\Automaton'$, it must also
  exist in every intermittent product on the way to $\Automaton'$, and if $\Map$
  is consistent for intermittent transition labels as it must be, then neither the intermittent $\Image$ predicates nor the final one can be the source of the unsatisfiability.

  This leaves one final potential source of unsatisfiability: the first half of
  \Materialise{}: \BindingSum{}. For that to be unsatisfiable, it requires
  intermittent automata $\Automaton_l, \Automaton_r$ such that adding
  $\BindingSum(\Automaton_l \times \Automaton_r)$ is unsatisfiable. The
  generated equations state that the transitions of $\Automaton_l$ and
  $\Automaton_r$ must be used precisely as often as their corresponding results
  in $\Automaton_l \times \Automaton_r$. For this set of equations to be
  unsatisfiable there must exist no path through $\Automaton_l \times
  \Automaton_r$ that preserves this. However, this is true from the definition
  of the product of automata: since we know the product to be nonempty, it must
  in some sense contain at least one path whose equivalent exists in both
  $\Automaton_l$ and $\Automaton_2$ and cannot use a corresponding transition
  more often, or it would recognise a different langauge. Hence no such case
  exists.
\end{proof}

Since it follows from \cref{lma:multi:linclude,lma:multi:rinclude} that both
variants of the predicate are precisely equally strong, it must mean that they
are equivalent, and we have proven the correctness as defined in
\cref{def:multiple}.
\end{proof}

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  A common problem in string constraint solvers is computing the Parikh image, a
   set of linear equations that describe all possible combinations of character
   counts in strings of a given language. Automata-based string solvers
   frequently need to compute the Parikh image of large products (intersections)
   of nondeterministic automata, which in many operations is both prohibitively
   slow and memory-intensive. We contribute a novel understanding of how Parikh
   maps can be tackled as a constraint solving problem to solve real-world
   constraints stemming from functions on regular languages, most notably the
   length constraint. Furthermore, we show how this formulation can be
   efficiently implemented as a calculus, \Calculus{}, in an automated theorem
   prover supporting Presburger logic.  We implement \Calculus{} in a tool
   called \Catra{}, and evaluate it on constraints produced by the
   \OstrichPlus{} string constraint solver when solving Parikh automata
   intersection problems produced when solving standard string constraint
   benchmarks involving string length constraints. We show that our solution
   strictly outperforms the standard approach described
   in~\citeauthor{generate-parikh-image} as well as the over-approximating
   method recently described by~\citeauthor{approximate-parikh} by a wide
   marigin, and for realistic timeouts for constraint solving also the~\Nuxmv{}
   model checker.
\end{abstract}

@@

The key ideas of \Calculus{} is a combination of problem-aware case splitting,
lazy enforcement of automata connectivity, and lazy computation of products.

@@

We implement \Calculus{} as a theory for the \Princess{} automated theorem
prover in the tool \Catra. \Catra also supports the approximate method of
\cite{approximate-parikh}, its fall-back variant adapted
from~\cite{generate-parikh-image}, and an adapter for the \Nuxmv{} model
checker~\cite{nuxmv}. Using \Catra, we compare \Calculus{} to the other two
back-ends on \NrBenchmarks{} Parikh automata intersection problems generated by
\OstrichPlus{} when solving the PyEx string constraint benchmark suite involving
string length constraints \cite{pyex}.

@@

To keep things simple, in this first example we let $f$ be the function that
gives the length of a given string; $f\left(\text{curious and curiouser
still}\right) = 27$, and $f\left(\text{homo}\right) +
f\left(\text{morphism}\right) = f\left(\text{homomorphism}\right) = 12$, and we
let $\varphi(\MonoidElement) = \exists k \HoldsThat m = 2k + 1 \land k \geq 0$,
i.e. require that the length of the string is odd.

@@

The na\"ive approach would be to first compute the product of the automata, then
use the approach from \cite{generate-parikh-image} to find its image under $f$,
and then solve the constraints in an automated theorem prover. However, we can
take advantage of both the constraints and definitions of $f$ to prune the
automata before computing the product and help reduce the blow-up.

@@

For our constraint, we will use $\TransitionCount{a} > \TransitionCount{b}$,
that is finding a count of characters in a string accepted by both automata where
there are more a:s than b:s. Since the underlying calculus is the same, we start immediately from \cref{fig:example-simplify-1}.

@@

\section{Projections on Parikh Maps}\label{sec:generalised}

@@

Observe that every homomorphism~$\Map:\: \Sigma^* \to \Monoid$ can be
represented as the composition~$h' \circ \ParikhMap$, for some
homomorphism~$h' : \Naturals^k \to M$. One of the insights underlying our
approach is that it is more efficient to directly compute a
projection on the Parikh image~$\Map(\Language)$, than to first compute the
standard image~$\ParikhMap(\Language)$ followed by projection to
some property of interest.

@@

One such simplifying homomorphism can express string
length, the problem that originally motivated our study of the Parikh
map. This mapping is relevant when solving constraints that combine
language membership as well as word length, for instance the formula
\begin{equation}\label{eq:stringLength}
x \in \Language_1 \wedge y \in \Language_2 \wedge |x| > |y|
\end{equation}
mentioned in the introduction. To solve this formula, let
$\Monoid = \Naturals$, and define the homomorphism~$L$ by $L(a) = 1$
for all characters~$a \in \Alphabet$. The length of a string
$s = s_1 \RepeatSum{\Concat} s_n$ is given by
$L(s) = \sum L(s_i) = 1 \RepeatSum{+} 1 = n$, and to solve
\eqref{eq:stringLength} we can instead solve the equi-satisfiable
formula~$\alpha \in L(\Language_1) \wedge \beta \in L(\Language_2)
\wedge \alpha > \beta$. This paper proposes efficient native
procedures to reason about membership constraints
like~$\alpha \in L(\Language_1)$, avoiding the computation of
the complete image~$L(\Language_1)$.

@@

Parikh images are also applicable for deciding more general classes of
string constraints~\cite{ostrich-plus}. Consider, for instance, a
constraint involving the substring operation:
\begin{equation}
  \label{eq:substring}
  x \in \Language_1 \wedge \; 0 \leq n \leq m \leq |x| \wedge x[n:m] \in \Language_2
\end{equation}
in which $x$ is a string variable, $n, m$ are integer variables, and
$x[n:m]$ denotes the substring of $x$ starting at position~$n$ running
until position~$m$. This constraint belongs to an expressive fragment
of string logic that cannot be decided by most state-of-the-art string
solvers. To illustrate the decision procedure proposed in
\cite{ostrich-plus} for string constraints of this kind, suppose that
$\Language_2$ is defined by the regular
expression~$\mathtt{(ab|c)*}$. An automaton recognising this language
is shown in \cref{fig:parikh-automata} (left).

@@

\section{A Calculus for Projections on Parikh Images}\label{sec:calculus}

@@

We present the rules of \Calculus{} for one automaton in
\cref{tbl:rules:single}. Note that we operate on sets of
formulas. Additionally, we also use the convention of splitting the
formulas into linear equations and inequalities ($\SomeInequalities$)
and other formulas ($\SomeClause$). We assume that our predicates $\Image$ and $\Connected$ only occur positively.

The filtering function~$\Filter$ is evaluated symbolically, and can in practice
be read as a function from transitions to $\Naturals$-valued terms
(e.g.~\texttt{t} or~\texttt{t+1}). In our implementation \Catra{}, described in
\cref{sec:implementation}, $\Filter$~is a vector of fresh variables with the
same size as~$\Transitions$.

@@

\subsubsection{The rules in \cref{tbl:rules:single} are solution-preserving}

\begin{lemma}\label{lma:single-correct}
  Consider an application of one of the rules in
  \cref{tbl:rules:single}, with
  premises~$\SomeClause_1, \ldots, \SomeClause_k$ and
  conclusion~$\SomeClause$. An assignment~$\beta$ satisfies the
  conclusion~$\SomeClause$ if and only if it satisfies one of the
  premises~$\SomeClause_i$.
\end{lemma}

@@

  \Expand{} unfolds the definition of the $\Image$ predicate. To show
  that the rule is solution-preserving we prove the equivalence of the
  upper and lower sets of formulas:
  \begin{itemize}
  \item Assume that $\beta$ satisfies the conclusion, which means that
    there is some accepting path
    $\Path = \PathEnumeration \in \Accepting{\Paths(\Automaton)}$ with
    $\val_\beta(\Filter(\Transition)) = \TransitionCount(\Transition,
    \Path)$ and $\val_\beta(\MonoidElement) =
    \Map(\WordOf(\Path))$. Since immediately implies that $\beta$
    satisfies $\Connected(\Automaton, \Filter)$, since a path is
    connected, and $\FlowEq(\Automaton, \Filter)$ since an accepting
    path satisfies the flow equations. The
    equation~$\MonoidElement = \sum_{\Transition \in
      \Transitions_\Automaton}\Filter(\Transition) \cdot
    \Map(\Transition)$ holds because of
    $\val_\beta(\Filter(\Transition)) = \TransitionCount(\Transition,
    \Path)$.
  \item Assume that $\beta$ satisfies the premise, which implies that
    $\val_\beta(\Filter)$ describes a consistent, connected flow of
    the automaton. By the same argument as in
    \cite{generate-parikh-image} (\cref{sec:verma}), this flow
    can be mapped to an accepting path~$\Path$ of $\Automaton$ such
    that each transition~$\Transition$ occurs on $\Path$ exactly
    $\val_\beta(\Filter(\Transition))$ times. Together with the equation
    $\val_\beta(\Filter(\Transition)) = \TransitionCount(\Transition,
    \Path)$, this implies that $\beta$ satisfies $\SinglePredicateInstance$.
  \end{itemize}

@@

\subsection{Correctness of \Calculus{} for Products of Automata}

Since \cref{tbl:rules:multi} only extends the existing rules of
\cref{tbl:rules:single}, we only have to prove termination and solution
preservation for the new rules.

\subsubsection{\Calculus{} for products of automata terminates}
\begin{lemma}\label{lma:multi-terminates}
  Suppose $\SomeClause{}$ is a set of formulas in which the product
  version of $\Image$ only occurs positively. There is no
  infinite sequence of proofs~$P_0, P_1, P_2, \ldots$ in which $P_0$
  has $\SomeClause{}$ as root, and each $P_{i+1}$ is derived from
  $P_i$ by applying one of the rules in \cref{tbl:rules:multi}.
\end{lemma}

\begin{proof}
  The rule~\ExpandM{} can only be applied finitely often since its side condition only allows applying it once per instance of an $\Image$ predicate containing a product, and the only rule that introduces a new $\Image$ predicate with a product, $\Materialise$ does so with non-overlapping automata from the $\Image$ predicate it removes. Therefore, the number of automata in $\Image$ predicates is strictly decreasing.

  The rule \Materialise{} can similarly only be used finitely many times, as
  each application reduces the number of automata in the product of $\Image$ by
  one automaton, until only one remains and \cref{lma:single-terminates} for
  single-automaton instances applies.
\end{proof}

\subsubsection{The rules in \cref{tbl:rules:multi} are solution-preserving}

\begin{lemma}\label{lma:multi-correct}
  Consider an application of one of the rules in
  \cref{tbl:rules:multi}, with
  premises~$\SomeClause_1, \ldots, \SomeClause_k$ and
  conclusion~$\SomeClause$. An assignment~$\beta$ satisfies the
  conclusion~$\SomeClause$ if and only if it satisfies one of the
  premises~$\SomeClause_i$.
\end{lemma}

  \ExpandM{} applies \Expand{} to every automata $\Automaton_i$ of the product. 
  \begin{itemize}
  \item Assume that $\beta$ satisfies the conclusion, which means that
    there is some accepting path in the product $\Automaton_1 \times \ldots \times \Automaton_k$ such that
    $\Path = \PathEnumeration \in \Accepting{\Paths(\Automaton_1 \times \ldots \times \Automaton_k)}$ with
    $\val_\beta(\Filter(\Transition)) = \TransitionCount(\Transition,
    \Path)$ and $\val_\beta(\MonoidElement) =
    \Map(\WordOf(\Path))$. That immediately implies that every automaton $\Automaton_i$ would satisfy its $\Image{}$ constraints individually, and hence also the constraints generated by \ExpandM{}. \Fudge{Missing Materialise!}    
  \item Assume that $\beta$ satisfies the premise, which implies that
    $\val_\beta(\Filter)$ describes a consistent, connected flow of
    the automaton. By the same argument as in
    \cite{generate-parikh-image} (\cref{sec:verma}), this flow
    can be mapped to an accepting path~$\Path$ of $\Automaton$ such
    that each transition~$\Transition$ occurs on $\Path$ exactly
    $\val_\beta(\Filter(\Transition))$ times. Together with the equation
    $\val_\beta(\Filter(\Transition)) = \TransitionCount(\Transition,
    \Path)$, this implies that $\beta$ satisfies $\SinglePredicateInstance$.
  \end{itemize}
